### 2025-01-08 paper/icml25/first/sects/shacpp.tex
added evaluation (WIP)
chore: minors on shac++ flow

In practice, this is achieved by caching the state-action-reward triplets obtained from the environment and then training the neural network to minimize the MSE loss. That is, we minimize the loss $\mathcal{L}_\theta^{R}:\mathcal{T}^N\rightarrow\mathbb{R}$:
$$ \frac{1}{\left|B\right|}\sum_{s,a,r \in B}\left|\left| R_\theta(s, a) - \underbrace{r}_{\hat{R}(s, a)} \right|\right|^2 $$
Where $B$ represents a batch of state-action-reward triplets sampled uniformly from the cache.

@@

    Where $\alpha$ is a hyper-parameter that controls the strength of the penalty. In our experiments, we set $\alpha=1$. Usually, actions are either clipped to the allowed action space or, an activation function (such as hyperbolic tangent or sigmoid) is used to ensure that the actions are within the allowed range. This is acceptable for PPO and SHAC. However, in our scenario, this penalty is crucial. To understand why, consider that we are training the policy to optimize two neural networks that approximate the environment. Further, these networks are never trained outside the allowed action range. As a result, it is likely that these networks will be maximized outside the allowed range thus pushing the policy to generate actions far outside the allowed range. This can ultimately result in 0-gradients when action clipping is applied or high pre-activation actions when activation function is used.

@@

And, to minimize the time spent between swapping among the different training procedures (policy, value, reward, transition), we apply a cool-down of $K^V$/$K^R$/$K^F$ episodes between running training procedure for the value/reward/transition networks.

@@

\begin{algorithm}[t]
    \begin{algorithmic}[1]
    \STATE Initialize $\pi_\theta,V_\theta,R_\theta,W_\theta$ networks
    \STATE Initialize learning rates $\eta_\pi, \eta_R, \eta_V, \eta_W$
    \STATE Initialize environment $\mathcal{E}$
    \STATE Initialize $\gamma, \alpha$
    \FOR{episode in $1, \ldots, N_{\text{episodes}}$}

@@

        \STATE $\pi_\theta \gets \pi_\theta - \eta_\pi \nabla \mathcal{L'}^\pi_\theta(\hat{r},\hat{v},\gamma,\alpha)$
        \STATE $V_\theta \gets V_\theta - \eta_V \nabla \mathcal{L}^V_\theta(\hat{v},s,v)$
        \STATE $R_\theta \gets R_\theta - \eta_R \nabla \mathcal{L}^R_\theta(\hat{r},s,r)$
        \STATE $W_\theta \gets W_\theta - \eta_W \nabla \mathcal{L}^F_\theta(\hat{s},s,a)$

>>>>

In practice, this is achieved by leveraging a \emph{replay buffer} to cache the state-action-reward triplets obtained from the environment. The neural network is then trained to minimize the MSE loss. Specifically, we minimize the loss $\mathcal{L}_\theta^{R}:\mathcal{T}^N\rightarrow\mathbb{R}$:
$$ \frac{1}{\left|B\right|}\sum_{s,a,r \in B}\left|\left| R_\theta(s, a) - \underbrace{r}_{\hat{R}(s, a)} \right|\right|^2 $$
Where $B$ represents a batch of state-action-reward triplets sampled uniformly from the cache.

@@

    Where $\alpha$ is a hyper-parameter that controls the strength of the penalty. In our experiments, we set $\alpha=1$. Usually, actions are either clipped to the allowed action space or, an activation function (such as hyperbolic tangent or sigmoid) is used to ensure that the actions are within the allowed range. While this approach is acceptable for algorithms like PPO and SHAC, the penalty we employ is crucial in our specific scenario. This necessity arises from the fact that we are training the policy to optimize two neural networks that serve as environment approximations. Because these networks are never trained with data outside the permissible action space, they are likely to be maximized beyond these bounds. Consequently, the policy may generate actions far outside the allowed range. This can ultimately result in 0-gradients when action clipping is applied or high pre-activation actions when activation function is used.

@@

Additionally, to minimize the time spent between swapping among the different training procedures (policy, value, reward, transition), we apply a cool-down of $K^V$/$K^R$/$K^F$ episodes between running training procedure for the value/reward/transition networks.

@@

\begin{algorithm}[t]
    \begin{algorithmic}[1]
    \STATE Initialize $\pi_\theta,V_\theta,R_\theta,F_\theta$ networks
    \STATE Initialize learning rates $\eta_\pi, \eta_R, \eta_V, \eta_F$
    \STATE Initialize environment $\mathcal{E}$
    \STATE Initialize $\gamma, \alpha$
    \FOR{episode in $1, \ldots, N_{\text{episodes}}$}

@@

        \STATE $\pi_\theta \gets \pi_\theta - \eta_\pi \nabla \mathcal{L'}^\pi_\theta(\hat{r},\hat{v},\gamma,\alpha)$
        \STATE $V_\theta \gets V_\theta - \eta_V \nabla \mathcal{L}^V_\theta(\hat{v},s,v)$
        \STATE $R_\theta \gets R_\theta - \eta_R \nabla \mathcal{L}^R_\theta(\hat{r},s,r)$
        \STATE $F_\theta \gets F_\theta - \eta_F \nabla \mathcal{L}^F_\theta(\hat{s},s,a)$
